---
title: "p8105_hw1_cz2689"
output: github_document
date: "2022-09-24"
---
```{r}
library(tidyverse)
```

---

# Problem 1
```{r}
data("penguins", package = "palmerpenguins")
view (penguins)
skimr::skim(penguins)
nrow(penguins)
ncol(penguins)
```
This data set is called penguins, and it includes variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. This data set has 344 rows and 8 columns. 
And the mean flipper length is 200.92 according to the 'skimr' function. 

## Plot the penguins data

```{r}
ggplot(penguins, aes(x = bill_length_mm , y = flipper_length_mm, colour = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 6, width = 6)
```

# Problem 2

```{r}
p2 = tibble(
  norm = rnorm(10),
  logi = norm > 0,
  char = c("a","b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fact = factor(c("t", "m", "b", "t", "m", "b", "t", "m", "b", "m"))
  )
p2
```

## Taking the mean of each variable

```{r}
a = pull(p2, var = norm)
mean(a, var = norm)

b = pull(p2, var = logi)
mean(b, var = logi)

c = pull(p2, var = char)
mean(c, var = char)

d = pull(p2, var = fact)
mean(d, var = fact)
```

As we can see from the output, we can compute mean for only numeric and logical vector but not for character and factor vector.







